\documentclass[12pt]{article}
\usepackage{statproj}

\title{Statistical Analysis of the Relationship Between Website Page Size and Load Time}
\author{Avigyan Chakraborty (BS2516)}
\date{November, 2025}

\begin{document}

% First page with title, name, date, and abstract
\maketitlepage{\thetitle}{\theauthor}{\thedate}{
% Your abstract content will go here
This is where you'll write your abstract content later. You can replace this text with your actual abstract when you're ready. The abstract should provide a brief overview of your statistics assignment, including the main objectives, methods, and key findings.

You can write multiple paragraphs here. The formatting will handle the spacing and make it look professional and well-organized for your statistics assignment.
}

% Second page with table of contents (clickable links and improved spacing)
\makecontents

% Third page - start your project here
\section{Introduction}
Your content starts here. This section will introduce your statistical analysis project and its significance.

\section{Data Description}

The dataset used in this project was generated using
an automated script which reads the list of websites from
\texttt{website\_list.json} and makes five HTTP requests
to each site and records two key metrics for each attempt:

\begin{itemize}
  \item \textbf{Page load time (in seconds):}
    The total time required
    for the page to fully load under a web-browser instance.
  \item \textbf{Page size (in kilobytes):}
    The total size of loaded
    webpage including all its resources.
\end{itemize}

These raw measurements were then dumped into
\texttt{website\_load\_data.json} which was then piped into
the script \texttt{make\_avg\_csv.py} which calculates
the average of five entries for each website and then
writes the data into \texttt{averaged\_data.csv}
in a structured manner.

\end{document}
